Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-05 WRITEUP/response.md

We thank the referee for providing constructive and thoughtful
comments to improve the manuscript. We have addressed all the concerns
raised by the referee and details can be found in the revised version
-- please see attached. A brief description on how we incorporated the
changes can be found below.

1a) We have changed the title to ".... of the strongly lensed quasar host galaxy RXS\,J1131-1231"

1b) To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".

1c) We have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).

1d) We have changed "dynamical information" to "kinematic information".
- reconstruct the intrinsic gas dynamics --> reconstruct the intrinsic line profile and source-plane velocity structure

We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify our message to the reader.

### 2016-11-05 WRITEUP/table_magFactor.tex
added DR's comments, major change: gas fraction, sSFR, intro and conclusion, and removed 'nuclear SB'
update velocity

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Channel} &
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
126$-$130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.6ex] %which is source 1 and 2 then?
131$-$135 & 7.6 $\pm$ 1.6 & \\ [0.6ex] % would this be source 1 or 2?
136$-$140 & 8.7 $\pm$ 2.0 & \\ [0.6ex]
141$-$145 & 4.1 $\pm$ 0.9 & \\ [0.6ex]
146$-$150 & 4.2 $\pm$ 0.6 & \\ [0.6ex]
151$-$155 & 4.3 $\pm$ 2.4 & \\ [0.6ex]
156$-$160 & 3.1 $\pm$ 0.9 & \\ [0.6ex]
weighted average & 4.4 & \\ [0.6ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{Source 1 is RXJ1131 and source 2 is its companion. See text for details.}
\end{deluxetable}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
346\,$-$\,260       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ 
238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.7ex]\hline
131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-84,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
\end{deluxetable}
